True Lies

### 2018-11-05 GSV-comment-brief.Rmd
Submitted version

GSV argue that existing sample sizes may be too small to reject "no lying" ($\lambda = 0). 
We can check this with the Bayesian method by simulations. With a uniform prior and an $N$ of 100, 
the Bayesian method has `r pct_format(power_l_25)` power to detect $\lambda$ of 25% and 
`r pct_format(power_l_10)` power to detect $\lambda$ of 10%. So, on this we agree.

@@

pp <- MASS::fitdistr(nats$prop_liars, "beta", start = list(
        shape1 = 1, shape2 = 1
      ))
pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])

@@

pp <- MASS::fitdistr(banerjee$N_gt3/banerjee$N, "beta", start = list(
        shape1 = 1, shape2 = 1
      ))
pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])

@@

@banerjee2018spillover use the GSV method to estimate confidence intervals for proportion of liars
in a die roll task. They estimate the proportion of liars who report a die roll above 3 
($P = 0.5$), for several treatments. Table \ref{tab:banerjee-recalc} shows GSV confidence intervals,
along with recalculated Bayesian confidence intervals, and confidence intervals for the difference
between lying to the "Same" and "Other" caste. I use a uniform prior rather than a pooled prior
here. This may be more reasonable when we are testing for differences in experimental treatments,
as we do not start from a strong belief that the treatments have no effect.

The Bayesian confidence intervals are much larger
than GSV confidence intervals. Only a couple of significant results survive. (Note that
significance tests in the original paper were done with standard frequentist techniques, not the
GSV method.) More importantly, it is clear that the N is rather low to make useful inferences
about the differences between groups. For example, for the T2-winners-GC group in the "aligned
payoffs" treatment, differences in lying could be as much as 30% in either direction. Notice
also that sometimes confidence intervals for the number of liars start above 0, even though less
than half reported the high outcome. This is because, starting from a pooled prior, the evidence
from the low N is not enough to shift the prior much. Low die rolls are more likely than a population
of truth tellers.

@@

1. Do not use the GSV confidence intervals, unless you are specifically interested in *Lies* rather
  than $\lambda$. Even in that case, be aware that the confidence intervals have low coverage for 
  extreme values of *R*.

2. Do not use the GSV estimates. They are biased as estimators of both *Lies* and $\lambda$.

3. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
  confidence intervals and tests.

4. If your N is small, consider Bayesian estimates and confidence intervals. To estimate differences 
  between subgroups, consider empirical Bayes with a prior derived from the pooled sample.

@@

Figure \ref{fig:gsv-lies-coverage-pic} shows the proportion of confidence intervals that contain the true
value of *Lies*. Coverage is shown by confidence level, *N*, *P* and the decile (within these groups) of
proportion of heads reported (*R/N*). Overall results are quite solid, but when the proportion of
heads reported is low or high, coverage drops below the nominal intervals. Interestingly, this problem
gets worse as $N$ increases.

>>>>

GSV argue that existing sample sizes may be too small to reject "no lying" ($\lambda = 0$). 
We can check this with the Bayesian method by simulations. With a uniform prior and an $N$ of 100, 
the Bayesian method has `r pct_format(power_l_25)` power to detect $\lambda$ of 25% and 
`r pct_format(power_l_10)` power to detect $\lambda$ of 10%. So, on this we agree.

@@

pp <- suppressWarnings(MASS::fitdistr(nats$prop_liars, "beta", start = list(
        shape1 = 1, shape2 = 1
      )))
pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])

@@

# didn't converge to give finite density at 0!
# pp <- suppressWarnings(MASS::fitdistr(pmax(0.03, 2 * banerjee$N_gt3/banerjee$N - 1), "beta", start = list(
#         shape1 = 1, shape2 = 1
#       )))
# pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])

@@

@banerjee2018spillover use the GSV method to estimate confidence intervals for proportion of liars
in a die roll task. They estimate the proportion of liars who report a die roll above 3 
($P = 0.5$), for several treatments. Table \ref{tab:banerjee-recalc} shows GSV confidence intervals,
along with recalculated Bayesian confidence intervals, and confidence intervals for the difference
between lying to the "Same" and "Other" caste. Here, I used a non-informative prior rather than
a pooled prior, letting the algorithm maintain an "open mind" about treatment effects.

The Bayesian confidence intervals are much larger
than GSV confidence intervals. Only a couple of significant results survive. (Note that
significance tests in the original paper were done with standard frequentist techniques, not the
GSV method.) More importantly, it is clear that the N is rather low to make useful inferences
about the differences between groups. For example, for the T2-winners-GC group in the "aligned
payoffs" treatment, differences in lying could be as much as 40% in either direction.

@@

1. Do not use the GSV method. Confidence intervals are always too narrow, risking false inferences.

2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
  confidence intervals and tests.

3. If your N is small, consider Bayesian estimates and confidence intervals. To estimate differences 
  between subgroups, consider empirical Bayes with a prior derived from the pooled sample.

@@

Figure \ref{fig:gsv-lies-coverage-pic} shows the proportion of confidence intervals that contain the true
value of *Lies*. Coverage is shown by confidence level, *N*, *P* and the decile (within these groups) of
proportion of heads reported (*R/N*). Overall results are quite solid, but when the proportion of
heads reported is low or high, coverage drops below the nominal intervals. This is probably because,
at these extremes, the difference between the true posterior and equation \ref{eqn:truncated-binom} 
becomes large. Interestingly, this problem gets worse as $N$ increases.
